---
title: "MA615 Text Mining Task II Report"
author: "Yifeng He"
date: "2021/12/05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=F,message = F,echo=F,highlight=F)
pacman::p_load(
tidyverse,
magrittr,
knitr,
gutenbergr,
tidytext,
sentimentr
)
```

## Task I Book Choice

The book I chose is 'The Origin of The Family, Private Property and the State' by Friedrich Engles.

```{r}
my_book=gutenberg_download(c(33111))
write.table(my_book,'Book2.txt',row.names = F)

```

```{r}
library(tnum)
tnum.authorize("mssp1.bu.edu")
tnum.setSpace("test2")
source("Book2TN-v6A-1.R")
```

```{r}
mybook<-read.table('Book2.txt')
```

## TASK II

In this task, I will first use three methods to analyze 'The Origin of The Family, Private Property and the State'. The sentiment analysis includes "AFINN", "BING", "NRC". For the extra credit, I will use "Loughran-McDonald" for another sentiment analysis. 

The content for this book is about early human history and reveal the destruction of old social rules; the development of new society based on private property. Engles first discusses the development of family, from blood-related family to monogamy family. Then he talks about the foundation of Germany and Rome; next he states specialization and social class and the start and end of countries. Engles discussed marriage, slaves, social progress, and human rights. As a result, more positive words appear in the book than negative words. 

As shown in the below code chunks and graphs, more positive words appear in the book than negative ones. However, in some chapters, Engles talks about the dissemble of nations and the situation of slaves. These result in the increase of negative words and the downward bars in the sentiment analysis. 

```{r}
#my_book=mybook
engles_book <- my_book %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  unnest_tokens(word, text)
```


```{r}
afinn <- engles_book %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")
```



```{r}
afinn <- engles_book %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
  engles_book %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  engles_book %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```

```{r fig.cap="sentiment plot"}
#form the book
bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")+
  theme_bw()
```

```{r}
#from the book
bing_word_counts <- engles_book %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
```

```{r fig.cap="nega-posi words count"}
bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)+
  theme_bw()
```



```{r fig.cap='Word Cloud Graph'}
library(wordcloud)

engles_book %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```



```{r fig.cap="sentiment word cloud"}
#
library(reshape2)
engles_book %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("red", "blue"),
                   max.words = 120)
```

This is the part for extra credit:

```{r}
#another method for sentiment analysis
FE<-tidy_books %>% 
    inner_join(get_sentiments("loughran")) %>%
    mutate(method = "Loughran-McDonald")  %>% 
  count(method, index = linenumber %/% 80, sentiment) %>% 
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

FE%>%ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +labs(title='Loughran-McDonald')+
  theme_bw()+theme(plot.title = element_text(hjust = 0.5))
```





## TASK III

### tnum

First I put the book into the tnum database.
	
```{r}
#upload the book
# tnBooksFromLines(mybook$V2, "hvdsb/book4")
```

```{r}
sb12<- tnum.query('hvdsb/book4/section# has text',max=8000) %>% tnum.objectsToDf()
engles_sent<-sb12 %>% separate(col=subject,
                  into = c("path1", "path2","section","paragraph","sentence"),
                  sep = "/",
                  fill = "right") %>%
  select(section:string.value)

#change the string values of 0001 to 1, to simple numeric values
engles_sent<-engles_sent %>% mutate_at(c('section','paragraph','sentence'),~str_extract_all(.,"\\d+") %>% unlist() %>% as.numeric())

#get from the sentimentr github
engles_result<-engles_sent %>% dplyr::mutate(sentence_split = get_sentences(string.value))%$%
    sentiment_by(sentence_split, list(section))

#the sentiment analysis graph of the the book rank from high to low
plot(engles_result)

#the emotional curve for the book
plot(uncombine(engles_result))
```

### Comparison with TASK II


```{r}
#Change from task two "divided by 80" to by chapters.
new_bing<-engles_book %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al.") %>%
    count(method, index = chapter, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% mutate(sentiment = positive - negative)


#standardize the scale of sentiment for task 2 and task 3 for comparison
bing2_rep<-new_bing %>% mutate(engles_scale=scale(sentiment)) %>% select(method,index,engles_scale)
colnames(bing2_rep)[2]='section'

engles_result<-engles_result %>% mutate(sentimentr_scale=scale(ave_sentiment))

#join together two tasks into one data frame
engles_res_2<-left_join(engles_result,bing2_rep,by='section')%>% select(section,engles_scale,sentimentr_scale)
engles_res_plot<-engles_res_2 %>% pivot_longer(cols=c('sentimentr_scale','engles_scale'),names_to = 'sentiment')

#the graph for comparison
engles_res_plot %>%ggplot(aes(y=value,x=factor(section))) +
  geom_bar(aes(fill=factor(sentiment)),stat='identity',position = "dodge",width = 0.7)+theme_bw()

```

